Simple repression draft

### 2020-10-16 doc/resubmission/section_03_beyond_means.tex
remove challenging so et al phrase

The simplest model of constitutive expression that we can imagine is shown as
model 1 in Figure~\ref{fig2:constit_cartoons}(A) and assumes that transcripts
are produced as a Poisson process from a single promoter state. This is the
picture from Jones et.\ al.~\cite{Jones2014} that was used to interpret a
systematic study of gene expression noise over a series of promoters designed to
have different strengths, but no regulation. This model insists that the
``true'' steady-state mRNA distribution is Poisson, implying the Fano factor
$\nu$ must be 1. In~\cite{Jones2014}, the authors carefully attribute measured
deviations from Fano = 1 to intensity variability in fluorescence measurements,
gene copy number variation, and copy number fluctuations of the transcription
machinery, e.g., RNAP itself. In this picture, all the corrections to Poisson
behavior are derived as additive corrections to the Fano factor. For challenging
the ``universal noise curve'' from So et.\ al.~\cite{So2011}, this picture was
excellent. It is appealing in its simplicity, with only two parameters, the
initiation rate $r$ and degradation rate $\gamma$. In other words, the model is
not excessively complex for the data at hand. But for many interesting
questions, for instance in the recent work~\cite{Razo-Mejia2020}, attributing
all deviations from the model to extrinsic noise sources, limits the kinds of
predictions that can be done. To make progress then we need a (slightly) more
complex model than model 1 that would allow us to incorporate the non-Poissonian
features of constitutive promoters directly into a master equation formulation.

>>>>

The simplest model of constitutive expression that we can imagine is shown as
model 1 in Figure~\ref{fig2:constit_cartoons}(A) and assumes that transcripts
are produced as a Poisson process from a single promoter state. This is the
picture from Jones et.\ al.~\cite{Jones2014} that was used to interpret a
systematic study of gene expression noise over a series of promoters designed to
have different strengths, but no regulation. This model insists that the
``true'' steady-state mRNA distribution is Poisson, implying the Fano factor
$\nu$ must be 1. In~\cite{Jones2014}, the authors carefully attribute measured
deviations from Fano = 1 to intensity variability in fluorescence measurements,
gene copy number variation, and copy number fluctuations of the transcription
machinery, e.g., RNAP itself. In this picture, all the corrections to Poisson
behavior are derived as additive corrections to the Fano factor. This picture is
appealing in its simplicity, with only two parameters, the initiation rate $r$
and degradation rate $\gamma$. In other words, the model is not excessively
complex for the data at hand. But for many interesting questions, for instance
in the recent work~\cite{Razo-Mejia2020}, attributing all deviations from the
model to extrinsic noise sources, limits the kinds of predictions that can be
done. To make progress then we need a (slightly) more complex model than model 1
that would allow us to incorporate the non-Poissonian features of constitutive
promoters directly into a master equation formulation.
